Appendix S1: Supporting Tables and Figures

### 2021-09-21 ms/SI.Rmd
Finish fixing caption letters per AJB
Upper-case
No parentheses in figure

a + b + c +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

```{r envir, fig.width = 7, fig.height = 9}
# Define function for plotting environment
plot_env <- function(part, label, var_select, fill_lab = "", labels = ggplot2::waiver()) {
  ggplot() +
    geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
    geom_sf(data = biodiv_ferns_spatial, aes(fill = .data[[var_select]]), color = "transparent") +
    geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** {label}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") + 
    labs(fill = fill_lab) +
    scale_fill_scico(palette = "lajolla", labels = labels) +
    scale_x_continuous(guide = guide_axis(check.overlap = TRUE)) +
    theme_grey(base_size = 10) +
    theme(
      panel.grid.major = element_line(color = "grey60", size = 0.1),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      axis.ticks = element_blank(),
      axis.text = element_text(color = "grey60"),
      axis.title = element_blank(),
      legend.position = "right",
      legend.title = element_markdown()
    )
}

@@

a <- ggplot() + 
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = abundance), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_scico(palette = "lajolla", label = k) +
  labs(fill = "No. specimens") +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(A)**</span>", hjust = "inward", vjust = "inward", color = "white") + 
  map_theme()

b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = redundancy), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "Redundancy") +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(B)**</span>", hjust = "inward", vjust = "inward", color = "white") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm")) +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

@@

a + b + c + 
  plot_layout(nrow = 1) +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

a + b + c + d +
  plot_layout(ncol = 2, nrow = 2) +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

a + b +
  plot_layout(ncol = 2) +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

# Use the ggtree::`%<+%` operator to map the bootstrap values onto the ggtree object
ggtree(dendro_tax, size = 0.15) %<+% 
  cluster_nodes_tax_tbl +
  aes(color = cluster) +
  scale_color_manual(
    values = bioregion_cols[c(1,2,3,4,"Other")], breaks = c(1,2,3,4,"Other"), name = "Cluster", na.value = "grey10") +
  theme(legend.position = "right") +
  labs(subtitle = "**(A)** Taxonomic") +
  theme(plot.subtitle = element_markdown())
```

@@

# Use the ggtree::`%<+%` operator to map the bootstrap values onto the ggtree object
ggtree(dendro_phy, size = 0.15) %<+% 
  cluster_nodes_phy_tbl +
  aes(color = cluster) +
  scale_color_manual(
    values = bioregion_cols[c(1,2,3,4,"Other")], breaks = c(1,2,3,4,"Other"), name = "Cluster", na.value = "grey10") +
  theme(legend.position = "right") +
  labs(subtitle = "**(B)** Phylogenetic") +
  theme(plot.subtitle = element_markdown())
```

@@

  ggplot() +
    geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
    geom_sf(data = genus_abun, aes(fill = richness), color = "transparent") +
    geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** *{genus_select}*</span>"), 
      hjust = "inward", vjust = "inward", color = "white") + 
    labs(fill = "Richness") +
    scale_fill_scico(palette = "lajolla") +
    scale_x_continuous(guide = guide_axis(check.overlap = TRUE)) +
    theme_grey(base_size = 10) +
    theme(
      panel.grid.major = element_line(color = "grey60", size = 0.1),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      axis.ticks = element_blank(),
      axis.text = element_text(color = "grey60"),
      axis.title = element_blank(),
      legend.position = "right",
      legend.title = element_markdown()
    )
}

@@

wrap_plots(modelfit_plot_list) +
  guide_area() +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

a + b + plot_annotation(tag_levels = "A",
                        tag_prefix = "(",
                        tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

```{r protected-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of protected areas and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
# pass the dots to filter data
make_protected_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.07, fill = "white") +
    geom_sf(data = protected_areas %>% mutate(status = str_to_sentence(status)), aes(fill = status), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.12) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = protection_cols, name = "Protection status") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}

@@

```{r deer-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of areas with deer and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
make_deer_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.07, fill = "white") +
    geom_sf(data = deer_range %>% filter(range == "estimated") %>% mutate(range = str_to_sentence(range)), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "2003"), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "1978"), aes(fill = range), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.12) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = deer_cols, name = "Range data source") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}

>>>>

a + b + c +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "",
                  tag_suffix = "") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

```{r envir, fig.width = 7, fig.height = 9}
# Define function for plotting environment
plot_env <- function(part, label, var_select, fill_lab = "", labels = ggplot2::waiver()) {
  ggplot() +
    geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
    geom_sf(data = biodiv_ferns_spatial, aes(fill = .data[[var_select]]), color = "transparent") +
    geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**{part}** {label}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") + 
    labs(fill = fill_lab) +
    scale_fill_scico(palette = "lajolla", labels = labels) +
    scale_x_continuous(guide = guide_axis(check.overlap = TRUE)) +
    theme_grey(base_size = 10) +
    theme(
      panel.grid.major = element_line(color = "grey60", size = 0.1),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      axis.ticks = element_blank(),
      axis.text = element_text(color = "grey60"),
      axis.title = element_blank(),
      legend.position = "right",
      legend.title = element_markdown()
    )
}

@@

a <- ggplot() + 
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = abundance), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_scico(palette = "lajolla", label = k) +
  labs(fill = "No. specimens") +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**A**</span>", hjust = "inward", vjust = "inward", color = "white") + 
  map_theme()

b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = redundancy), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "Redundancy") +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**B**</span>", hjust = "inward", vjust = "inward", color = "white") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm")) +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

@@

a + b + c + 
  plot_layout(nrow = 1) +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "",
                  tag_suffix = "") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

a + b + c + d +
  plot_layout(ncol = 2, nrow = 2) +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "",
                  tag_suffix = "") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

a + b +
  plot_layout(ncol = 2) +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "",
                  tag_suffix = "") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

# Use the ggtree::`%<+%` operator to map the bootstrap values onto the ggtree object
ggtree(dendro_tax, size = 0.15) %<+% 
  cluster_nodes_tax_tbl +
  aes(color = cluster) +
  scale_color_manual(
    values = bioregion_cols[c(1,2,3,4,"Other")], breaks = c(1,2,3,4,"Other"), name = "Cluster", na.value = "grey10") +
  theme(legend.position = "right") +
  labs(subtitle = "**A** Taxonomic") +
  theme(plot.subtitle = element_markdown())
```

@@

# Use the ggtree::`%<+%` operator to map the bootstrap values onto the ggtree object
ggtree(dendro_phy, size = 0.15) %<+% 
  cluster_nodes_phy_tbl +
  aes(color = cluster) +
  scale_color_manual(
    values = bioregion_cols[c(1,2,3,4,"Other")], breaks = c(1,2,3,4,"Other"), name = "Cluster", na.value = "grey10") +
  theme(legend.position = "right") +
  labs(subtitle = "**B** Phylogenetic") +
  theme(plot.subtitle = element_markdown())
```

@@

  ggplot() +
    geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
    geom_sf(data = genus_abun, aes(fill = richness), color = "transparent") +
    geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**{part}** *{genus_select}*</span>"), 
      hjust = "inward", vjust = "inward", color = "white") + 
    labs(fill = "Richness") +
    scale_fill_scico(palette = "lajolla") +
    scale_x_continuous(guide = guide_axis(check.overlap = TRUE)) +
    theme_grey(base_size = 10) +
    theme(
      panel.grid.major = element_line(color = "grey60", size = 0.1),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "transparent"),
      axis.ticks = element_blank(),
      axis.text = element_text(color = "grey60"),
      axis.title = element_blank(),
      legend.position = "right",
      legend.title = element_markdown()
    )
}

@@

wrap_plots(modelfit_plot_list) +
  guide_area() +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A",
                  tag_prefix = "",
                  tag_suffix = "") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

a + b + plot_annotation(tag_levels = "A",
                        tag_prefix = "",
                        tag_suffix = "") &
  theme(plot.tag = element_text(face = "bold"))
```

@@

```{r protected-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of protected areas and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
# pass the dots to filter data
make_protected_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.07, fill = "white") +
    geom_sf(data = protected_areas %>% mutate(status = str_to_sentence(status)), aes(fill = status), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.12) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**{part}** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = protection_cols, name = "Protection status") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}

@@

```{r deer-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of areas with deer and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
make_deer_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.07, fill = "white") +
    geom_sf(data = deer_range %>% filter(range == "estimated") %>% mutate(range = str_to_sentence(range)), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "2003"), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "1978"), aes(fill = range), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.12) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**{part}** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = deer_cols, name = "Range data source") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}
